---
title: "lab3"
author: "JungHyun Troy Cheon"
date: "June 8, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Importing the Data
Run install the package `readr` by running `install.packages("readr")` in the console.

The code below reads in the `tents.csv` comma-separated file.  The `col_types` argument is telling `R` what the data type is in each column.  See `?read_csv` if you're curious.
```{r}
library(readr)
tents <- read_csv("tents.csv", col_types = "ccnniccc")
```

### Questions
Answer the following questions programatically.  Some questions ask for you to explain what you see---you may answer this as text outside a code block.

1. Run `str()` on `tents`.  What information does it tell you? This is a useful function to know.
```{r}
str(tents)
```
It tells me 90 obs. of 8 variables and classes of each data.frame
2. What class is `tents`?
```{r}
class(tents)
```

3. How many rows are in `tents`?
```{r}
nrow(tents)
```
It has 90 rows

4. How many columns are in `tents`?
```{r}
ncol(tents)
```
It has 8 columns
5. What are the names of the columns?
```{r}
names(tents)
```
it has names brand price weight height bestuse seasons capacity
6. Display the first 5 rows.
```{r}
tents[1:5,]
```

7. Display the last 4 rows.
```{r}
tents[86:90,]
```

8. Find out how to use `quantile` to find the interquartile range (75th percentile - 25th percentile) of the weights of the tents.
```{r}
tents$weight
duration = tents$weight
quantile(duration,0.75)-quantile(duration,0.25)
q <- quantile(duration)
q
IQR(q)

```

9. Find the standard deviation of the heights of the `tents`.  Does `R` use `n` or `n-1` in the denominator when calculating standard deviation?
```{r}
duration1 = tents$height
sd(duration1)
?sd
```
use a help function to see if r uses n or n-1. r uses n-1

10. The weight is given in grams.  Add a new column to the data frame called `weight_lbs` that contains the weight of the tents in pounds.  Remember to overwrite `tents` with your update.
```{r}
fram <-data.frame(tents)
weight_lbs <- fram$weight/453.592
weight_lbs
cc <- cbind(fram, weight_lbs)
cc
```

11. The height is given in centimeters.  Add a new variable `height_in` to the data frame that contains the height of the tents in inches. Remember to overwrite `tents` with your update.
```{r}
height_in <- fram$height/2.54
height_in
hh <- cbind(cc, height_in)
hh
```

12. How many tents cost more than $400?
```{r}
pri <- tents$price > 400
sum(pri)
```
22!

13. Subset the data frame so that it only contains tents that are valued $300 or less.  Assign the subsetted data frame the name `so_cheap_tents`.
```{r}
so_cheap_tents <- tents[tents$price < 300, ]

so_cheap_tents
```

14. Of the tents that are more than $300, what percent are `big-agnes` tents?
```{r}
over300 <- tents[tents$price >300,]
sum(over300$brand == "big-agnes")
nrow(over300)
percent <- 15/52
percent
```


15. Select the `bestuse` column of `tents` in four different ways: using `$`, `[[]]`, position number and `[]`, and variable name and `[]`. 
```{r}
tents$bestuse
tents[["bestuse"]]
tents[,6]
tents[,"bestuse"]        
```

16. What is the name of the tend with the best height-to-weight ratio?
```{r}
mmm <- which.max(tents$height/tents$weight)

tents$name[mmm]
```

17. Run `table` with two arguments, `seasons` and `capacity` (this should be one table).  What did it do?
```{r}
table(tents$seasons, tents$capacity)
```
it gave me 3 rows and 5 columns matrix

18. What type of tent (bestuse) is the most common? Your answer should return only the use and not the count.
```{r}
be <- table(tents$bestuse)
which.max(be)
names(be)[which.max(be)]
```


19. Create a data frame called `kelty` with only data on kelty tents.  Do the same for `big-agnes`.  Then, combine the two data frames.
```{r}
kelty <-tents[tents$brand == "kelty",]
bigagnes <- tents[tents$brand == "big-agnes",]
rbind(kelty,bigagnes)

```
